On the number of tiles visited by a\\ line segment on a rectangular grid

### 2021-12-30 paper.tex
Scale in Figure ratio_asympt_slopes
Wording ("line" could be confusing)

\emph{MSC2020:} 52C99, 60D05. % ***Alex: is there a better one?
% 52C99: Discrete geometry: None of the above, but in this section
% 60D05: Geometric probability and stochastic geometry
\end{abstract}

@@

% ***Alex: please check this, as I've done some content changes
Lastly, $\Pr[i \geq 2]$ as computed in Proposition~\ref{prop: Pr i} can be interpreted as the probability of crossing at least one line in Buffon's experiment. Indeed, for $n=2$ the third line in \eqref{eq: Pr i geq n} reduces again to $2\len/(\pi a)$ for $\len \leq a$, whereas the second line reduces to $2\len f(a/\len)/(\pi a)$ for $\len > a$. Using \eqref{eq: f} this is expressed as
\[
\frac 2 \pi \arccos\frac a \len + \frac{2\len}{\pi a} \left(1 - \sqrt{1-\frac{a^2}{\len^2}} \right),
\]
in agreement with the known result for Buffon's needle problem with $\len > a$ \cite[theorem 1.1.2]{Mathai99}. On the other hand, $\Pr[i \geq n]$ for $n \geq 3$ can be seen as the probability of crossing at least one line in a modified version of Buffon's setting in which a needle endpoint is only allowed to move in a narrower region in the middle of a strip, of width $2n-3$ times smaller than the strip width.

@@

% ***Change vertical axis scale: [0 1]? [0.5 1]?
\begin{figure}
\centering%
\includegraphics[width=.7\textwidth]{ratio_asympt_slopes}%
\caption{Asymptotic ratio of average and maximum numbers of visited tiles
}%
\label{fig: ratio asympt slopes}%
\end{figure}%

>>>>

\emph{MSC2020:} 52C99, 60D05.
% 52C99: Discrete geometry: None of the above, but in this section
% 60D05: Geometric probability and stochastic geometry
\end{abstract}

@@

% ***Alex: please check this, as I've done some content changes
Lastly, $\Pr[i \geq 2]$ as computed in Proposition~\ref{prop: Pr i} can be interpreted as the probability of crossing at least one line in Buffon's experiment. Indeed, for $n=2$ the third expression in \eqref{eq: Pr i geq n} reduces again to $2\len/(\pi a)$ for $\len \leq a$, whereas the second reduces to $2\len f(a/\len)/(\pi a)$ for $\len > a$. Using \eqref{eq: f} this is expressed as
\[
\frac 2 \pi \arccos\frac a \len + \frac{2\len}{\pi a} \left(1 - \sqrt{1-\frac{a^2}{\len^2}} \right),
\]
in agreement with the known result for Buffon's needle problem with $\len > a$ \cite[theorem 1.1.2]{Mathai99}. On the other hand, $\Pr[i \geq n]$ for $n \geq 3$ can be seen as the probability of crossing at least one line in a modified version of Buffon's setting in which a needle endpoint is only allowed to move in a narrower region in the middle of a strip, of width $2n-3$ times smaller than the strip width.

@@

\begin{figure}
\centering%
\includegraphics[width=.7\textwidth]{ratio_asympt_slopes}%
\caption{Asymptotic ratio of average and maximum numbers of visited tiles
}%
\label{fig: ratio asympt slopes}%
\end{figure}%
